Genome-wide changes in expression during inflorescence architecture development

### 2015-07-29 ms.Rmd
regenerating genome index for 50b SE reads

---
title: "Template for writing scientific papers in R markdown"
author: "Tom Harrop"
csl: csl/the-plant-journal.csl
output:
  html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    theme: cerulean
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
  word_document:
    fig_caption: yes
bibliography: bib/test.bib
---

# Abstract

lorem ipsum :)

# Methods

Doing stuff [@Hrycay:2009ua]. Even more stuff [@Ren:2013jv]. @Harrop:2014dg disagrees. @Engstrom:2013cx wrote a nice paper about RNASeq mapping tools.

@@

>>>>

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
output:
  word_document:
    fig_caption: yes
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
  html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    theme: cerulean
bibliography: bib/test.bib
---

Authors:

Addresses:

### Running title

### Keywords

### SRA details for libaries

Word count

***

# Summary

# Significance statement

# Introduction

* Rice inflorescence development
+ branching & grain yield
+ sequential changes in meristem activity
+ few key genes

# Results

## Dissections in early stages of inflorescence development
+  **Figure**: laser microdissections

## Transcriptome sequencing of meristem samples
+ Short (boring) section about sequencing stats
+ **Table** (or supplementary): # reads, mapping %, rRNA, introns, genes blah blah

## Clustering of expression patterns
+ **Figure**: Gene expression clusters
+ GO enrichment?
+ Clusters including 'known' genes

## Patterns of expression of transcription families
+ **Figure**: GSEA of transcription factor families

## MADS genes: comparison of expression & homology in rice, tomato, arabidopsis
+ **Figure**: Similarity tree of MADS proteins with expression values and dN/dS values for each one.

# Discussion

# Experimental procedures

# Accession Numbers

# Acknowledgements

# Short legends for Supporting Information

@@

***

# Tables

***

# Figure legends

***

# Figures

***

# Junk

I think `inline code` should work?
